\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2018-06-04 doc/USER_MANUAL/06_fault_sources.tex
documented cohesion in slip-weakening friction

\item [{\&\textbf{INIT\_STRESS}}] input block sets the initial fault stresses
relative to the foot-wall side of the fault. Initial stresses are
composed of a constant background value possibly overwritten in prescribed
regions by heterogeneous distributions (see \&\textbf{DIST2D} blocks
below):

\begin{description}
\item [{S1}] = constant background value of along-strike shear stress (positive
in the usual strike direction)
\item [{S2}] = constant background value of along-dip shear (positive is
down-dip, normal faulting)
\item [{S3}] = constant background value of normal stress (negative in
compression)
\item [{n1}] = number of heterogeneous items for along-strike shear stress
{[}default is 0{]}
\item [{n2}] = number of heterogeneous items for along-dip shear stress
{[}default is 0{]}
\item [{n3}] = number of heterogeneous items for normal stress {[}default
is 0{]}
\end{description}
\item [{\&\textbf{SWF}}] input block sets the slip-weakening friction parameters
of the fault:

\begin{description}
\item [{mus}] = constant background value of static friction coefficient
\item [{mud}] = constant background value of dynamic friction coefficient
\item [{dc}] = constant background value of critical slip-weakening distance
\item [{nmus}] = number of heterogeneous items for static friction coefficient
{[}default is 0{]}
\item [{nmud}] = number of heterogeneous items for dynamic friction coefficient
{[}default is 0{]}
\item [{ndc}] = number of heterogeneous items for critical slip-weakening
distance {[}default is 0{]}\\

\end{description}

\item [{\&\textbf{RSF}}] input block sets the rate and state friction parameters
of the fault:

\begin{description}
  \item []
    We refer to the well known rate and state friction formula:
    $$\mu = f_0 + a* log(\frac{v}{v_0}) + b* log(\frac{v_0}{\theta L}))  $$
\item [{V0}] = constant background value of $V_0$
\item [{f0}] = constant background value of $f_0$
\item [{a}] = constant background value of $a$
\item [{b}] = constant background value of $b$
\item [{L}] = constant background value of $L$
\item [{V\_init}] = constant background value of along strike right lateral slip rate at time 0
\item [{theta\_init}] = constant background value of state variable $\theta$ at time 0
\item [{C}] = constant background value of cohesion (in Pa)
\item [{StateLaw}] = 1 or 2. 1 for aging law , 2 for slip law with strong dynamic weakening.
\item [{n**}] = number of heterogeneous items for quantity **
\end{description}

@@

\end{lyxlist}
\begin{lyxlist}{00.00.0000}
\item [{\textbf{DATA/rsf\_hete\_input\_file.txt}}]  Heterogeneous stresses and friction input for
  rate and state friction.
To activate this feature, in Par\_file\_faults name list \&\textbf{RUPTURE\_SWITCHES}, set RSF\_HETE=.TRUE..

  The format of  {\textbf{DATA/rsf\_hete\_input\_file.txt}} is as such, in the first line there are four integers

  that are sequentially documenting the number of divisions along strike, number of divisions along

  dip, cell size along strike , cell size along dip. Then the following N(N=NumberOfDivisionsAlongStrike

  * NumberOfDivisionsAlongDip) lines will document the stress and friction properties on the grid.

  There are a total of 13 columns.
  \begin{enumerate}
  \item{Column1} = Along strike distance(m)

>>>>

\item [{\&\textbf{INIT\_STRESS}}] input block sets the initial fault stresses
relative to the foot-wall side of the fault. Initial stresses are
composed of a constant background value possibly overwritten in prescribed
regions by heterogeneous distributions (see \&\textbf{DIST2D} blocks
below):
\begin{description}
\item [{S1}] = constant background value of along-strike shear stress (positive
in the usual strike direction)
\item [{S2}] = constant background value of along-dip shear (positive is
down-dip, normal faulting)
\item [{S3}] = constant background value of normal stress (negative in
compression)
\item [{n1}] = number of heterogeneous items for along-strike shear stress
{[}default is 0{]}
\item [{n2}] = number of heterogeneous items for along-dip shear stress
{[}default is 0{]}
\item [{n3}] = number of heterogeneous items for normal stress {[}default
is 0{]}
\end{description}

\item [{\&\textbf{SWF}}] input block sets the slip-weakening friction parameters
of the fault:
\begin{description}
\item [{mus}] = constant background value of static friction coefficient
\item [{mud}] = constant background value of dynamic friction coefficient
\item [{dc}] = constant background value of critical slip-weakening distance
\item [{C}] = constant background value of cohesion (in Pa)
\item [{nmus}] = number of heterogeneous items for static friction coefficient
{[}default is 0{]}
\item [{nmud}] = number of heterogeneous items for dynamic friction coefficient
{[}default is 0{]}
\item [{ndc}] = number of heterogeneous items for critical slip-weakening
distance {[}default is 0{]}
\item [{nC}] = number of heterogeneous items for cohesion
\end{description}

\item [{\&\textbf{RSF}}] input block sets the rate and state friction parameters
of the fault:
\begin{description}
  \item []
    We refer to the well known rate and state friction formula:
    $$\mu = f_0 + a* log(\frac{v}{v_0}) + b* log(\frac{v_0}{\theta L}))  $$
\item [{V0}] = constant background value of $V_0$
\item [{f0}] = constant background value of $f_0$
\item [{a}] = constant background value of $a$
\item [{b}] = constant background value of $b$
\item [{L}] = constant background value of $L$
\item [{V\_init}] = constant background value of along strike right lateral slip rate at time 0
\item [{theta\_init}] = constant background value of state variable $\theta$ at time 0
\item [{C}] = constant background value of cohesion (in Pa)
\item [{StateLaw}] = 1 or 2. 1 for aging law , 2 for slip law with strong dynamic weakening.
\item [{n**}] = number of heterogeneous items for quantity **
\end{description}

@@

\end{lyxlist}
\begin{lyxlist}{00.00.0000}
\item [{\textbf{DATA/rsf\_hete\_input\_file.txt}}]  Heterogeneous stresses and friction input for
  rate and state friction.
To activate this feature, in Par\_file\_faults name list \&\textbf{RUPTURE\_SWITCHES}, set RSF\_HETE=.TRUE..
  The format of  {\textbf{DATA/rsf\_hete\_input\_file.txt}} is as such, in the first line there are four integers
  that are sequentially documenting the number of divisions along strike, number of divisions along
  dip, cell size along strike , cell size along dip. Then the following N (N=NumberOfDivisionsAlongStrike
  * NumberOfDivisionsAlongDip) lines will document the stress and friction properties on the grid.
  There are a total of 13 columns.
  \begin{enumerate}
  \item{Column1} = Along strike distance(m)
